Machine Learning and Constraint Programming for Relational-To-Ontology Schema Mapping

### 2018-04-29 stp/paper/main.tex
Added one more citation

\ignore{We have developed a new approach for semantic labeling which can 
efficiently handle the \emph{unknown} class.}
\ignore{We demonstrate its efficiency by comparing against the state-of-the-art 
approach DSL~\cite{Pham:semantic}. } %Repeat from above
Tab.~\ref{tab:semlab} provides evidence that our new semantic labeling model is better suited for the task when there are unmatched attributes in domains.
DSL uses heuristic measures to capture the similarity of attributes within the same class, but 
unmatched attributes are clearly dissimilar from known semantic types, thus similarity measures may be unsound in the presence of unmatched attributes.
Our intuition as to why our approach performs better is that we have 
incorporated features which are derived directly from attribute values and are 
not based on the notion of similarity.
%\npr{Good enough explanation?}

>>>>

\ignore{We have developed a new approach for semantic labeling which can 
efficiently handle the \emph{unknown} class.}
\ignore{We demonstrate its efficiency by comparing against the state-of-the-art 
approach DSL~\cite{Pham:semantic}. } %Repeat from above
Tab.~\ref{tab:semlab} provides evidence that our new semantic labeling model is better suited for the task when there are unmatched attributes in domains.
DSL uses heuristic measures to capture the similarity of attributes within the same class, but 
unmatched attributes are clearly dissimilar from known semantic types, thus similarity measures may be unsound in the presence of unmatched attributes.
Our intuition as to why our approach performs better is that we have 
incorporated features which are derived directly from attribute values and are 
not based on the notion of similarity~\cite{ruemmele2018evaluating}.
%\npr{Good enough explanation?}
